---
Week 8 R Quiz
CUNY MS Data Analytics Summer Bridge Program
---

<b>Question 1: Illustrate how to add element by element the contents of two numeric vectors of equal length using a for loop:</b>

```{r}
vect.1 <- c(1,4,7,9,12,15)
vect.2 <- c(5,2,15,43,6,4)

if (length(vect.1) == length(vect.2))
{
  vect.3 <- c(1:length(vect.1))
  for (i in 1:length(vect.1))
  {
  vect.3[i] = vect.1[i] + vect.2[i]  
  }
} else
{ 
  print("Vectors are different lengths")
}

(vect.3)
```
<b>Q1A) Comment on how this differs from the easier vector addition method preferred in R.</b>
     <p>The usual method would be to simply write: vect.3 <- vect.1 + vect.2.  This is very fast and works as long as the two vectors are multiple lenghts of one another.  I beleive this is because R is a 'vectorized language' and such vector calculation a much more efficent in R.  Personally, I'm glad this is the case because years ago, I used to have to write loops for similar calculations</p>
     
<p><b>Question 2: Write code that uses a while loop that determines how many "heads" in a row an arbitrary vector of coin flips has starting at the beginning.</b></p><p>An example of a vector input is c("heads","heads","tails","heads"). Your code should give an answer of 2 when run on this vector. Note that a vector that begins with "tails" should give an answer of 0.</p>
```{r}
vect.flips <- c("heads","heads","tails","heads")
Nmbr.heads <- 0
for (i in 1:length(vect.flips))
{
  if (vect.flips[i] == "heads") { Nmbr.heads <- Nmbr.heads + 1}
}
(Nmbr.heads)
```

<p><b>Question 3: Use a for loop running over all 100 integers from 1 to 100 and the ifelse() function to add only the odd numbers from 1 to 100.</b></p>
```{r}

Nmbrs <- c(1:100)
running.total = 0

for (i in 1:length(Nmbrs))
{
  ifelse(Nmbrs[i] %% 2 == 0, running.total <- running.total + Nmbrs[i],running.total)
  # No need for ifelse() as the above line could be written more simply with just if:
  # if(Nmbrs[i] %% 2 == 0) {running.total <- running.total + Nmbrs[i]}
}

(running.total)
```
<p>BONUS: Can you show how to accomplish the same thing without using a loop?</p>
Yes - by using the properties of the modulus and vecotrization!

Any number mod 2 give you just a 1 or 0.  1 if it's ODD and 2 if it's even as seen here:
```{r}
(Nmbrs.2 <- Nmbrs %% 2)
```
Now we can simply use this to 'zero out' all the even integers:
```{r}
(Nmbrs.2 <- (Nmbrs %% 2) * Nmbrs)
```
And lastly, simply take the sum of the new vector:
```{r}
(sum(Nmbrs.2))
```
or much more simply:
```{r}
(sum((Nmbrs %% 2) * Nmbrs))
```