---
Week 8 R Assignment
CUNY MS Data Analytics Summer Bridge Program
---

<p>1.Use the rbinom() function with probability 0.5 to simulate a string of 100 coin flips.
```{r}
(coin.flips <- rbinom(100,1,0.5))
```
<p>2.Write code that will test the sequence you just generated to determine whether there is a string of at least seven in a row of either heads or tails. (You can choose whether to consider 0 heads and 1 tails or vice versa.)

My code is designed to end the loop as soon as it finds a 7 consecutive sequence of 0s or 1s in the data.  I'm defining Heads as 1s and Tails as 0s.  I tested the code extensively and I believe it works correctly. It sets 'SevenInARow' to 1 if it succeeds, otherwise it remains at 0.
```{r}
i <- 1
SevenInARow <- 0
sum.heads <- 0
sum.tails <- 0
while ((SevenInARow == FALSE) && i <= (length(coin.flips) - 6))
{
  sum.heads <- sum(coin.flips[i:(i+6)] == c(1,1,1,1,1,1,1))
  sum.tails <- sum(coin.flips[i:(i+6)] == c(0,0,0,0,0,0,0))
  if ((sum.heads == 7) || (sum.tails == 7))
  {
    SevenInARow <- 1
  }
  i <- i + 1
}
(SevenInARow)
```
<p>3.Enclose the code for steps 1 and 2 in a loop so that you can run it a bunch of times. Use this loop to determine the proportion of 100-toss sequences that actually have at least seven in a row of the same thing. This is your estimate of the probability.
<p>4.Run the loop with 10 such sequences. Then run it with 100, and 1000. (If you're really brave, run it more times still...)

Ok, so <b>'Seven.Tests.Num'</b> sets the number of tests to run and the vector <b>'Seven.Tests'</b> contains <b>0</b> or <b>1</b> depending on if the test for that set of 100 flips had seven consecutive heads or tails.  Then, we can simply look at the <b> Sum(Seven.Tests) / Length(Seven.Tests)</b> to estimate the probability.

```{r}

Seven.Tests.Num = 100
Seven.Tests <- c(1:Seven.Tests.Num)*0

for (j in 1:Seven.Tests.Num)
{
  coin.flips <- rbinom(100,1,0.5)
  i <- 1
  SevenInARow <- 0
  sum.heads <- 0
  sum.tails <- 0
  while ((SevenInARow == FALSE) && i <= (length(coin.flips) - 6))
  {
    sum.heads <- sum(coin.flips[i:(i+6)] == c(1,1,1,1,1,1,1))
    sum.tails <- sum(coin.flips[i:(i+6)] == c(0,0,0,0,0,0,0))
    if ((sum.heads == 7) || (sum.tails == 7))
    {
      SevenInARow <- 1
    }
    i <- i + 1
  }
Seven.Tests[j] = SevenInARow
}
(Seven.Tests)
(sum(Seven.Tests)/length(Seven.Tests))
```

<p>Comment both on how well your estimate seems to converge to a single answer and also how R performs at these loops. Do you notice a significant slowdown at 1000 sequences? What about 10,000? Where does your machine start really to grind to a halt?

My maching took about 53 seconds to do 100,000 loops of 100 Flips. This is my work computer and it's relatively new which is why this is pretty fast

I figure I'd put 400 trails of 1,000 tests to see if we're converging onto a number - basically, I just threw <i>another loop</i> around the above one and put the resutls into another vector :-)

Then to make things a little nicer to see, I put a the results into a simple data.frame and plotted them with a histogrm.  Looks to me like we're in the 0.54 to 0.55 range as to the probability:

```{r}

require(ggplot2)

Numbr.Tests <- 400
tests.numerators <- c(1:Numbr.Tests)*0

for (k in 1:Numbr.Tests)
{
  Seven.Tests.Num <- 1000
  Seven.Tests <- c(1:Seven.Tests.Num)*0
  
  for (j in 1:Seven.Tests.Num)
  {
    coin.flips <- rbinom(100,1,0.5)
    i <- 1
    SevenInARow <- 0
    sum.heads <- 0
    sum.tails <- 0
    while ((SevenInARow == FALSE) && i <= (length(coin.flips) - 6))
    {
      sum.heads <- sum(coin.flips[i:(i+6)] == c(1,1,1,1,1,1,1))
      sum.tails <- sum(coin.flips[i:(i+6)] == c(0,0,0,0,0,0,0))
      if ((sum.heads == 7) || (sum.tails == 7))
      {
        SevenInARow <- 1
      }
      i <- i + 1
    }
    Seven.Tests[j] = SevenInARow
  }
  tests.numerators[k] <- sum(Seven.Tests)  
}

TheResults <- data.frame(tests.numerators,Seven.Tests.Num, tests.numerators/Seven.Tests.Num)
head(TheResults)
hist(TheResults$tests.numerators/Seven.Tests.Num)
```