Sandesh Sadalge's Week 5 R Assignment
========================================================

<b> Question 1:</b> Appending vs. Pre-allocating in R:

So I didn't know much about this question and I'd like to do a lot more research into it.  I think the difference is that some data structures pre-allocate memory while others assign as needed.  I would think then that large calculations on pre-allocated structures would be faster but use more memory where as the oppsite is true with data structures that allocate as needed (less memory but possibly slower calculations on large amounts of data).

<b> Question 2:</b> Load the MASS package, look at the Boston data frame and make a new data frame with a few of those columns:

Load the MASS package:
```{r}
require(MASS)
```
Let's look at the Top 6 lines on the Boston dataset:
```{r}
head(Boston)
```
I looked at the description of the dataset and decided to make a dataframe based on the first 15 items (to keep this HTML small) in the following columns:

crim - Per Capita Crime Rate

age - proportion of owner-occupied units built prior to 1940

tax - full-value property-tax rate per \$10,000

medv median value of owner-occupied homes in \$1000s

```{r}
(newDF <- data.frame(crim = Boston$crim[1:15], age = Boston$age[1:15],tax = Boston$tax[1:15], medv = Boston$medv[1:15]))
```
