Sandesh Sadalge's Week 5 R Quiz
========================================================

<b>Question 1:</b> Make the Matrixes listed in the question:

```{r}
(A <- matrix(c(1,-1,-1,1), nrow =2))
(B <- matrix(c(2,3,-1,-2),nrow=2))
(C <- matrix(c(1,0,0,0),nrow=2))
(D <- matrix(c(0,1,0,1,0,0,0,0,1), nrow=3))
(E <- matrix(c(1,0,0,0,0,1,0,1,0),nrow = 3))
```

<b>Question 2:</b> Which one is idempotent?

According to the interwebs, a Matrix, M, is Idempotent iff M x X = M
So see which of the following results in a matric that is all TRUEs:
```{r}
(A == A %*% A)
(B == B %*% B)
(C == C %*% C)  # THIS ONE!
(D == D %*% D)
(E == E %*% E)
```

<b>Question3:</b> Which one is Orthogonal?

Again, according to what I researched using Google, a Martrix, M, is orthogonal iff M x Transpose(M) = I (Identity Matrix)

First, I made 2x2 & 3x3 Identity Matrixes:
```{r}
(TwoSqIdent <- matrix(c(1,0,0,1),nrow=2))
(ThreeSqIdent <- matrix(c(1,0,0,0,1,0,0,0,1),nrow=3))
```
Now to check is they're orthogonal i.e. see if Matrix X Transpose(Martix) = Identity (Again, see if they're all TRUE)
```{r}
(TwoSqIdent == A %*% t(A))
(TwoSqIdent == B %*% t(B))
(TwoSqIdent == C %*% t(C))
(ThreeSqIdent == D %*% t(D)) # THIS ONE!
(ThreeSqIdent == E %*% t(E)) # AND THIS ONE!
```

<b>Question 4:</b> Create a list with a vector, a matrix, an array, a dataframe and another list

First I made the various things asked for:
```{r}
vec <- c(1,2,3,4)
mtrx <- matrix(vec,nrow = 2)
arry <- array(1:24, c(2,2,3,2))
dtfrm <- data.frame(Numbers = 1:4, English = c("One","Two","Three","Four"), Spanish = c("Uno","Dos","Tres","Quatro"))
list2 <- list(1:3,1,mtrx)
```

Now here's the actual list asked for in the question:
```{r}
(theList <- list(vec,mtrx,arry,dtfrm,list2))
```
